---
title: "R Notes MarinStatsLectures"
output: html_notebook
---

All of these notes are taken from watching YouTube videos created by MarinStatsLectures - R Programming and Statistics. The playlist that these notes are curated from can be found [here](https://www.youtube.com/watch?v=riONFzJdXcs&list=PLqzoL9-eJTNBDdKgJgJzaQcY6OXmsXAHU&index=1 "Marin YouTube Playlist").

## Tutorial 1: Importing Data Into RStudio From a CSV / TXT File

\*\*\* If you ever need help with anything you can search the literature of a function using the below function calls \*\*\*

```{r}
help("read.csv")
?read.csv
```

Step 1: Save data from excel into CSV/TXT (CSV is recommended)

For CSV:

The **read.csv()** command takes two arguments, the **file** and if the top row is a **header**

In this case, instead of defiling a path for the **file** argument, we are calling the file.choose() function. This will trigger a popup screen at run-time to choose a file from your file explorer.

The **header** argument is a Boolean variable. If the first row of your data set has variable names / headers, **header=TRUE**. If the first row of your data set does not have variable names / headers, **header=FALSE**.

```{r}
dataset1 <- read.csv(file.choose(), header=TRUE)
print(dataset1)
```

Alternatively, the **read.table()** command can be used to import data from a CSV. The command operates the same as the previously mentioned read.csv() command, with one addition.

The third argument, \*\*sep="", notes the character separating the values in the list. In the case of a CSV,\*\* sep="," since the values are separated by commas.

```{r}
dataset2 <- read.table(file.choose(), header=TRUE, sep=",")
print(dataset2)
```

For TXT:

The process for importing TXT files is very similar to the process of importing CSV files. The only difference is that instead of using the read.csv() command you use the **read.delim()** command. Both commands take the same arguments.

```{r}
dataset3 <- read.delim(file.choose(), header=TRUE)
print(dataset3)
```

Alternatively, the **read.table()** command can be used to import data from a TXT. The only difference from the above instructions is that **sep** has a value of "\\t" for a tab instead of "," for a comma.

```{r}
dataset4 <- read.table(file.choose(), header=TRUE, sep="\t")
print(dataset4)
```

## Tutorial 2: Exporting Data from RStudio

The most flexible command for writing data is the **write.table** command. The **write.table** command takes 3 arguments, the **data** to be exported from R, the **file** to be exported to, denoted in quotations, and the **sep** argument, indicating the type of separation the file has.

```{r}
write.table(dataset1, file="testExport.csv", sep=",")
```

Note that saving a file this way will save it into our current working directory.

This will output a file with your given data, including row names. To omit row names, add the **row.names** field shown below and set it to false.

```{r}
write.table(dataset1, file="testExportNoNames.csv", row.names=FALSE, sep=",")
```

To save a file outside the current working directory simply specify a path in the **file** field. Note this example will not work on your machine until the path is adjusted to your file explorer desired path.

```{r}
write.table(dataset1, file="/Users/Trist/Desktop/TestNonCWDSave.csv", row.names=FALSE, sep=",")
```

Alternatively, we can use the **write.csv** command. It takes three arguments, **data**, **file,** and **row.names,** all with similar usages as above.

```{r}
write.csv(dataset1, file="testWritecsv.csv", row.names=FALSE)
```
